---
title: "ggplot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

**For more examples, see the [ggplot docs](http://ggplot2.tidyverse.org/index.html)**

All plots with ggplot start with code like below.

```{r, eval = FALSE}
ggplot(DATASET, aes())
```

For example,

```{r, eval = FALSE}
ggplot(mtcars, aes())
```

### What is `aes`?

The `aes()` function stands for aesthetic.
It tells ggplot how to put data on to a plot.
For example `ggplot(mtcars, aes(x = cyl, y = mpg))` says that `x` should be the `cyl` data from `mtcars`.

Adding Geoms
------------

Geoms are instructions for what action ggplot should take on each row.
For example, `geom_point` tells ggplot to go down each row, and put a dot.

```{r}
head(mtcars)
```


```{r, fig.width = 4, fig.height = 2.5}
ggplot(mtcars, aes()) +
  geom_point(aes(x = cyl, y = mpg))
```


Step by Step Problems
---------------------

### Scatterplot

**Fill in the plot below.**

```{r}
head(mtcars)
```


```{r, eval = FALSE}
ggplot(mtcars, aes()) +
  geom_point(aes(x = cyl, y = hp))
```

```{r, echo = FALSE}
ggplot(mtcars, aes()) +
  geom_point(aes(x = cyl, y = hp), alpha = 0) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())
```

<br><br><br><br>

### Scatterplot with Size and Shape

```{r}
head(mtcars)
```

```{r, eval = FALSE}
ggplot(mtcars, aes()) +
  geom_point(aes(x = wt, y = mpg, shape = cyl, size = hp))
```

```{r, echo = FALSE}
tcars <- transform(mtcars, cyl = factor(cyl))
ggplot(tcars, aes()) +
  geom_point(aes(x = wt, y = mpg, shape = cyl, size = hp), alpha = 0) +
  geom_point(aes(x = wt, y = mpg, shape = cyl, size = hp), alpha = 0, data = tcars)
```


### Facets

```{r}
head(mtcars)
```


```{r, eval = FALSE}
ggplot(mtcars, aes()) +
  geom_point(aes(x = wt, y = mpg)) +
  facet_grid(~ gear)

```

```{r, eval = TRUE}
ggplot(head(mtcars), aes()) +
  geom_point(aes(x = wt, y = mpg), alpha = 0) +
  facet_grid(~ gear)
```


### Simple Barchart

```{r}
newcars <- mtcars %>% 
  mutate(name = rownames(mtcars)) %>%
  select(name, name, hp)

head(newcars)
```

```{r}
ggplot(head(newcars), aes()) +
  geom_point(aes(x = name, y = hp)) +
  geom_col(aes(x = name, y = hp))
```


